---
title: 'Formula 1: Singapore Grand Prix Map'
author: "John Goodwin"
date: "5/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(leaflet)
library(rgdal)
library(magrittr)
```

```{r load_data, include=FALSE}
## Load GeoJSON
f1_circuits <- readOGR("f1-circuits-master/f1-circuits.geojson", encoding = "UTF-8", use_iconv = TRUE)
f1_locations <- readOGR("f1-circuits-master/f1-locations.geojson", encoding = "UTF-8", use_iconv = TRUE)

## Filter GeoJSONs to the Singapore GP data
f1_circuits$Name
selected_name <- "Marina Bay Street Circuit"
selected_circuit <- subset(f1_circuits, Name %in% selected_name)
selected_location <- subset(f1_locations, name %in% selected_name)
```

## Intro

This document leverages GeoJSON data from bacinger's f1-circuits repository as well as the `leaflet` R package to plot the location and circuit map for the Singapore Grand Prix--an annual race for Formula 1. A huge thanks to bacinger for putting these dataset's together and making them publiclly available! 

## Circuit Information
**Opened:** `r selected_location$opened` <br />
**First GP:** `r selected_location$firstgp` <br />
**Length:** `r selected_location$length`m <br />
**Altitude:** `r selected_location$alt`m <br />

## World Map
```{r world_map, echo=FALSE}
content <- paste(sep = '<br/>', 
                 paste0('<b>', selected_location$name, '</b>'),
                 selected_location$location)

selected_location %>%
  leaflet() %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addMarkers() %>%
  addPopups(popup = content,
            options = popupOptions(closeOnClick = FALSE)) %>%
  setView(0,0,2)

```

## Circuit Map

```{r circuit_map, echo=FALSE}
selected_circuit %>%
  leaflet() %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolylines(color = '#FF1801', opacity = 0.8)
```
